Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/sec-intro.tex

The measurement of double Higgs production will be one of the main
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC),
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta}.
%
Higgs pair production is directly sensitive to the
Higgs trilinear coupling $\lambda$~\cite{baglio}, and thus 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It is also sensitive to the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
In addition, Higgs pair production will also be a central process at
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Barr:2014sga} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

In the Standard Model (SM), the dominant mechanism for the production of two Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production~\cite{Dittmaier:2012vm}.
%
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once NNLL corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in gluon fusion have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta}.
%
While these studies differ in their qualitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
will only be achieved from the combination of various final states.

In addition to the gluon-fusion production mode, Higgs pairs
can be also produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja},
the associated production modes $hhW$ and $hhZ$, and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are extremely challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
Concentrating on the SM production dynamics of Higgs pair
production in the various channels, several studies
have investigate the interplay of various kinematical
distributions towards the optimisation of the
extraction of $\lambda$ from the measured
cross-sections, as well as the improvement
in the signal modeling taking into account
higher-order corrections and theoretical
uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza}
%

While the SM production rates for Higgs
pair production are small in all production modes,
and require the full integrated luminosity of the HL-LHC phase
to be accessed, double Higgs production rates can be substantially
enhanced in a variety of Beyond the SM (BSM) scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including effective theories with higher-dimensional
operators and anomalous values of the
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa},as well as
in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.

%
In many of these scenarios, the production rates are enhanced
and Higgs pair production becomes accessible already at
Run II, while still being consistent with current limits on BSM searches
and single Higgs coupling measurements.
%
With this motivation, searches for the production of Higgs pairs, whose rates
could be enhanced by BSM effects have already been performed
by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
and $b\bar{b}\gamma\gamma$~\cite{Aad:2014yja} final states,
and by
and CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
states.
%
though the sensitivity of these searches is still far from
that required for a SM production mechanism.
%
However, one should note that in general BSM dynamics modify substantially
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system, and therefore
different analysis strategies would be requires in BSM
Higgs pair searches as compared to SM production measurements.

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the the signal yield
is enhanced by the large branching fraction of Higgs bosons into bottom-anti-bottom
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However, a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background,
which makes it very challenging.
%
Previous studies of Higgs pair production in this
channel~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that with a luminosity of
3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}\sim 2.0$ can be obtained.
%
Both studies were based on exploiting the differences between signal and background
using techniques that account for a large number of kinematic
variables, Boosted Decision Trees
and Shower Reconstruction~\cite{Soper:2011cr} respectively.
%
Concerning the QCD multijet backgrounds, Refs.~\cite{Wardrope:2014kya,deLima:2014dta} the light-jet processes $bbjj$ and
$jjjj$,
which can fake the signal when 
some of the light jets are mistagged as $b$-jets.
%
As will show, this is not a good approximation since both due to
combinatorics and to $b$-quark radiation in the shower, the
contribution of $2b2j$ and $4j$ can become comparable
to that of $4b$.

In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $4b$ final state.
%
Our analysis is based on exploiting the differences between a large
number of kinematic variables in signal and background events.
%
Despite these large QCD multijet backgrounds, by combining the contribution of different final state
topologies, resolved, boosted and intermediate, with a careful optimization
of the analysis strategy, we find that it is possible to obtain a reasonable
good signal discrimination.
%
To further enhance the significance of the measurements, signal and background events
are processed using a Multivariate Analysis (in particular a feed-forward neural
network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0
%
Therefore, we are able to rescue the potential of this final state in a realistic
analysis setup.

One of the original motivations of this study was to provide guidance to the experiments
concerning which aspects of the measurement should be particularly optimized
to increase the signal significance in this channel.
%
In this respect, the study the dependence on our results on the $b$-tagging mistag
efficiency and the light and charm jet mistag rate, the jet energy and transverse
momentum resolution, or the Higgs invariant mass resolution.
%
In each of these cases, we determine the significance
$S/\sqrt{B}$ of the
measurement in both conservative and optimistic assumptions of these
parameters.

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the generation of the signal
and background Monte Carlo samples.
%
Then in Sect.~\ref{sec:analysis}
we describe our analysis strategy, and in particular
the classification of each individual event into
different categories according to the event topology.
%
The results for our traditional cut-based analysis
are presented in Sect.~\ref{sec:results}, and in
Sect.~\ref{sec:mva} we show how we can enhance signal
significance by means of multivariate techniques.
%
Finally in Sect.~\ref{sec:conclusions} we conclude and outline
possible future developments for Higgs pair production
in the $b\bar{b}b\bar{b}$ final state.

>>>>

The measurement of double Higgs production will be one of the main
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC),
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
%
Higgs pair production is directly sensitive to the
Higgs trilinear coupling $\lambda$~\cite{baglio}, and thus 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It is also sensitive to the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
While Standard Model (SM) cross-sections are small,
many Beyond the SM (BSM)
scenarios predict enhanced rates for double Higgs production, and
thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
and will continue at Run II.
%
In addition, Higgs pair production will also be a central process at
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

As in the case of single Higgs production,
in the SM the dominant mechanism for the production of a pair of Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production~\cite{Dittmaier:2012vm}.
%
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once NNLL corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in gluon fusion have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta}.
%
While these studies differ in their qualitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$
will only be achieved from the combination of various final states.

In addition to the gluon-fusion production mode, Higgs pairs
can be also produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes $hhW$ and $hhZ$~\cite{Barger:1988jk,baglio}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
Concentrating on the SM dynamics of Higgs pair production
in different channels, several studies
have investigate the interplay of various kinematical
distributions towards the optimisation of the
extraction of $\lambda$ from the measured
cross-sections, as well as the improvement
in the signal modeling taking into account
higher-order corrections and theoretical
uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha}.
%

While the SM production rates for Higgs
pair production are small in all production modes,
and require the full integrated luminosity of the HL-LHC phase
to be accessed, double Higgs production rates can be substantially
enhanced in a variety of Beyond the SM (BSM) scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including effective theories with higher-dimensional
operators and anomalous values of the
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.

%
In many of these scenarios, the production rates are enhanced
and Higgs pair production becomes accessible already at
Run II, while still being consistent with current limits on BSM searches
and single Higgs coupling measurements.
%
With this motivation, searches for the production of Higgs pair
have already been performed at Run I
by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
and $b\bar{b}\gamma\gamma$~\cite{Aad:2014yja} final states,
and by
CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
states.
%
One should note that in general BSM dynamics modify substantially
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system, and therefore
different analysis strategies would be requires in BSM
Higgs pair searches as compared to SM production measurements.

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into bottom-anti-bottom
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However, a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
channel~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that with a luminosity of
$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
%
These studies are
based on exploiting the differences between signal and background
using techniques that account for a large number of kinematic
variables, Boosted Decision Trees
and Shower Reconstruction~\cite{Soper:2011cr} respectively.
%
A limitation of these works is that
they do not account
 for the light-jet background processes $bbjj$ and
$jjjj$, which can fake the signal when 
some of the light jets are mistagged as $b$-jets.
%
As will show, this is not a good approximation since both due to
combinatorics and to $b$-quark radiation in the shower, the
contribution of $2b2j$ and $4j$ can become comparable
to that of the irreducible $4b$ component.

In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $4b$ final state.
%
 Our analysis is based on a combination of traditional cut-based
 methods with modern multivariate techniques
 (in particular feed-forward multi-layer neural networks),
 which lead to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
%
  Therefore, our strategy allow us to improve the
  potential of this final state even when considering a
  more realistic background modeling.

  One of the original motivations of this study was to provide guidance to the
  LHC experiments
concerning which aspects of the measurement should be particularly optimized
to increase the signal significance in the $4b$ channel.
%
In this respect, we study the dependence on our results on the $
b$-tagging mistag
efficiency, the light-jet mistag rate and the 
momentum resolution.
%
In each of these cases, we determine the signal significance
$S/\sqrt{B}$ of the
measurement in both conservative and optimistic assumptions of these
analysis settings.

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
and background processes using Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, and in particular
the classification of each individual event into
different categories according to their topology.
%
The results for the traditional cut-based analysis
are presented in Sect.~\ref{sec:results}, and in
Sect.~\ref{sec:mva} we show how we can enhance signal
significance using multivariate techniques.
%
The robustness of our results as function of our assumptions
on the $b$-tag rate, mistag probability and momentum
resolution in quantified in Ref.~\ref{sec:optimisation}.
%
Finally in Sect.~\ref{sec:conclusions} we conclude and outline
how our results can be extended to estimate the accuracy
in the determination of $\lambda$ and the constraints on
BSM scenarios in an EFT framework.

### 2015-07-13 paper/sec-mcsamples.tex

\section{Monte Carlo samples}
\label{mcgeneration}

@@

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
account.\footnote{We thank Eleni Vrodynou for assistance with di-Higgs production
  in {\tt MadGraph5\_aMC@NLO}.}
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

@@

%
Parton level events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
%
We use the default settings in the parton shower, in particular
we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We have switched off hadronisation, since this allows a more transparent modeling of
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
detector simulator, which is beyond the scope of this paper.
%
For a similar reason, we don't consider underlying event, multiple parton interactions and
pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia}.
%
The same applies to the background samples, which we discuss now.

@@

%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.71\times10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.12 \times10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.66 \times 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.71\times 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.51\times 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Summary of signal and background samples generated in this work,
  together with the corresponding generator-level LO cross-sections.
  %
  For top quark production, only the hadronic final state is generated.
  %
We also provide in each case the corresponding inclusive $K$-factor
  that is applied in each case to correctly normalize the distribution to the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Theoretical modeling of signal and background processes}
\label{mcgeneration}

@@

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

@@

%
Parton level events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
%
We use the default settings in the parton shower, in particular
we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We have switched off hadronisation, since this allows a more transparent modeling of
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
detector simulator, which is beyond the scope of this paper.
%
For a similar reason, we don't consider underlying event, multiple parton interactions and
pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba}.
%
The same applies to the background samples, which we discuss now.

@@

%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.71\times10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.12 \times10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.66 \times 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.71\times 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.51\times 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Summary of signal and background samples generated,
  together with the corresponding generator-level LO cross-sections.
  %
  For top quark production, only the hadronic final state is generated.
  %
We also provide in each case the corresponding inclusive $K$-factor
  that is applied in each case to correctly normalize the distribution to the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
